---
format:
  pdf:
    documentclass: article
    papersize: a4
    fontsize: 9pt
    geometry:
      - margin=1.5cm
      - top=1.2cm
      - bottom=1.4cm
    colorlinks: false
    pagestyle: empty
    header-includes:
      - \usepackage{booktabs}
      - \usepackage{array}
      - \usepackage{xcolor}
      - \definecolor{accent}{HTML}{0F6E63}
      - \definecolor{inkgrey}{HTML}{6A6A73}
      - \setlength{\parindent}{0pt}
params:
  payload: ""
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
p <- readRDS(params$payload)
# escape LaTeX-active characters in data-derived text (values may carry % and &)
esc <- function(x) {
  x <- gsub("\\\\", "\\\\textbackslash{}", x)
  x <- gsub("([%&#_])", "\\\\\\1", x)
  x
}
```

```{r title, results="asis"}
cat("```{=latex}\n")
cat(sprintf("\\begin{center}{\\LARGE\\bfseries %s}\\\\[2pt]{\\color{inkgrey} Release-day briefing --- %s}\\end{center}\n",
            esc(p$title), esc(p$source_line)))
cat("\\vspace{2pt}\\hrule\\vspace{6pt}\n")
cat("```\n")
```

```{r glance, results="asis"}
cat("```{=latex}\n")
cells <- vapply(p$glance, function(g)
  sprintf("\\begin{minipage}[t]{0.24\\textwidth}\\centering {\\color{inkgrey}\\small %s}\\\\[1pt]{\\Large\\bfseries\\color{accent} %s}\\end{minipage}",
          esc(g$label), esc(g$value)), "")
cat(paste(cells, collapse = "\\hfill"), "\n\n")
cat("\\vspace{4pt}\\hrule\\vspace{8pt}\n")
cat("```\n")
```

```{r charts, results="asis"}
cat("```{=latex}\n")
cat(sprintf("\\includegraphics[width=0.49\\textwidth]{%s}\\hfill\\includegraphics[width=0.49\\textwidth]{%s}\n\n",
            p$charts[1], p$charts[2]))
cat("\\vspace{4pt}\n")
cat("```\n")
```

```{r commentary, results="asis"}
cat("```{=latex}\n")
cat("{\\bfseries Commentary}\\\\[2pt]\n")
cat(paste(esc(p$commentary), collapse = " "), "\n\n")
cat("\\vspace{4pt}\n")
cat("```\n")
```

```{r table, results="asis"}
cat("```{=latex}\n")
tbl <- p$table
third_chart <- length(p$charts) >= 3
if (third_chart) cat("\\begin{minipage}[t]{0.55\\textwidth}\n\\vspace{0pt}\n")
if (!is.null(tbl) && nrow(tbl) > 0) {
  align <- paste0("l", paste(rep("r", ncol(tbl) - 1), collapse = ""))
  cat(sprintf("{\\footnotesize\n\\begin{tabular}{%s}\n\\toprule\n", align))
  cat(paste(esc(names(tbl)), collapse = " & "), "\\\\\n\\midrule\n")
  for (i in seq_len(nrow(tbl))) {
    cat(paste(esc(as.character(unlist(tbl[i, ]))), collapse = " & "), "\\\\\n")
  }
  cat("\\bottomrule\n\\end{tabular}\n}\n\n")
}
if (third_chart) {
  cat(sprintf("\\end{minipage}\\hfill\\begin{minipage}[t]{0.43\\textwidth}\n\\vspace{0pt}\n\\includegraphics[width=\\textwidth]{%s}\n\\end{minipage}\n",
              p$charts[3]))
}
cat("```\n")
```

```{r footer, results="asis"}
cat("```{=latex}\n")
cat("\\vfill\\hrule\\vspace{3pt}\n")
src <- if (identical(p$vintage_source, "wayback"))
  " (retrieved via Internet Archive mirror)" else ""
cat(sprintf("{\\scriptsize\\color{inkgrey} %s. Data retrieved %s%s. %s\\\\ %s}\n",
            esc(p$source_line), esc(p$retrieved), src,
            esc(p$revision_note), esc(p$attribution)))
cat("```\n")
```
